---
title: "MA213 Basic Statistics and Probability - Lab3 Activity"
bibliography: references.bib
link-citations: true
output:
  html_document:
    code_download: true 
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
```

## **Lab 3:** **Plotting and Summaries** activities

------------------------------------------------------------------------

### **New York Air Quality Dataset**

#### Q0. Import the `airquality.csv` file.

```{r}
#
#
# 
df <- read.csv("airquality.csv")
head(df)
names(df)
```

#### Q1. How is Ozone distributed? You want to look at the histogram of `Ozone`. Make a histogram of `Ozone` and assign it to `Hist_Ozone`. Then print it.

```{r}

```

#### Q2. How is Wind distributed? You are interested in looking at shape of `Wind`. This time create Box plot of `Wind` and Histogram of `Wind`.

```{r}


```

#### Q3. Let's compare those plots you obtained from Q2. What do you see and what are the differences? Think also about what you need to do more.

```{r}



```

#### Q4. Show the scatter plot of Solar radiation and Temperature. What are the patterns? Let's talk about it.

```{r}


```

#### Q5. Show the bar plot of average Solar radiation per each month. What do you see from the plot?

```{r}

```

### **Survival of Passengers on the Titanic**

#### Q6. Import the `titanic.csv` file.

```{r}

df2 <- read.csv("titanic.csv")
head(df2)
names(df2)
```

#### Q7. You are interested in how the data is categorized by sex visually. You are interested in seeing how many people in each category of `Sex`. Obtain the table showing `Sex` by `N` (how many people are counted in each category). Assign it to `table_data` and print it.

```{r}

```

#### Q8. Using this `table_data` variable, obtain pie chart.

```{r}

```

#### Q9. You are also interested in exploring whether age is associated with survival. How would you go about visualizing or summarizing this relationship?

```{r}

```

### Post-lab activities

Please name your submission as `lab3.R`

We are going to also analyze a synthetic data `somedata.csv`.

``` r
> head(my_df)
  X N        A    B     C        D E
1 1 1  1.42830 -5.0 25.00 4.945988 D
2 2 2  0.12983 -4.9 24.01 5.267488 E
3 3 3 -0.02932 -4.8 23.04 5.295265 E
4 4 4 -0.05000 -4.7 22.09 4.519594 C
5 5 5  0.71453 -4.6 21.16 3.943522 E
6 6 6 -0.35986 -4.5 20.25 4.860658 D
```

1.  load the `somedata.csv` file and assign it to `my_df` object.

2.  Get box plot of `A` in `my_df`. Looking at the box plot, how many suspected outliers can you see? assign it to `n_suspected` . (For example, you can do `n_suspected <- 1`).

3.  Obtain the scatter plot of `B` and `C` (x-axis for B, y-axis for C). What kind of relationship can you see? You can choose from those two

    `linear` , `nonlinear`

    You can answer this by assigning a variable `relationship` . (For example, you can do `relationship <- "linear"` or `relationship <- "nonlinear"` ).

4.  You are interested in looking at this mysterious variable `D` in the data. Look at the distribution of the data by producing a plot, answer if the shape of `D` is one of

    `right skewed` , `left skewed` , `uniform` , `symmetric`

    You can answer this by assigning a variable `shape` . (For example, you can do `shape <- "right skewed"` or `shape <- "uniform"` ... )

5.  Obtain a barplot of `E` in the data. If you create a barplot showing counts on Y axis and categories (from A to E) on X axis, what is the pattern of this barplot? You can answer if it is one of

    `increasing` , `decreasing` , `flat`

    You can answer this by assigning a variable `pattern` . (For example, you can do `pattern <- "increasing"` or `pattern <- "decreasing"` ... )
